---
title: "Titanic survival status study"
author: "Sun Huiyuan"
date: "2018Äê2ÔÂ14ÈÕ"
output: ioslides_presentation
---

```{r setup, echo=FALSE,message=FALSE}
library(tidyr)
library(datasets)
library(dplyr)
library(plotly)
data<-Titanic
data<-data.frame(data)
data<-spread(data,key=Survived,value=Freq)
```

## First Glance

This report is to show the study of survival status of Titanic incident
```{r,echo=FALSE,message=FALSE}
yaxs<-list(title="Survival Rate",titlefont=t,tickformat = "%")
addnewline<-function(plot,...){
  plot%>%group_by_(...)%>%summarise(Yes=sum(Yes),No=sum(No))%>%mutate(Survival_Rate=Yes/(Yes+No))
}
subplot(
  addnewline(data,"Class")%>%plot_ly(x=~Class,y=~Survival_Rate)%>%add_lines(name="by Class")%>%add_markers(showlegend=FALSE)%>%layout(yaxis=yaxs),
  addnewline(data,"Sex")%>%plot_ly(x=~Sex,y=~Survival_Rate)%>%add_lines(name="by Sex")%>%add_markers(showlegend=FALSE),
  addnewline(data,"Age")%>%plot_ly(x=~Age,y=~Survival_Rate)%>%add_lines(name="by Age")%>%add_markers(showlegend=FALSE),shareY=TRUE
)%>%layout(title="Titanic Survival Rate")
```

## Observations

- 1st Class survival rate is much higher than 2nd Class which is higher than 3rd Class and Crew
- Female and Child have higher survival rate
- We may want to explore whether all people from 1st and 2nd Class have higher survival rate?

## Further exploration

```{r,echo=FALSE,message=FALSE,warning=FALSE}

subplot(
filter(data,Class=="1st")%>%addnewline("Sex","Age")%>%plot_ly(x=~Age,y=~Survival_Rate)%>%add_lines(color=~as.factor(Sex))%>%add_markers(showlegend=FALSE,color=~as.factor(Sex))%>%layout(yaxis=yaxs),
filter(data,Class=="2nd")%>%addnewline("Sex","Age")%>%plot_ly(x=~Age,y=~Survival_Rate)%>%add_lines(color=~as.factor(Sex),showlegend=FALSE)%>%add_markers(showlegend=FALSE,color=~as.factor(Sex))%>%layout(title="2nd Class"),
filter(data,Class=="3rd")%>%addnewline("Sex","Age")%>%plot_ly(x=~Age,y=~Survival_Rate)%>%add_lines(color=~as.factor(Sex),showlegend=FALSE)%>%add_markers(showlegend=FALSE,color=~as.factor(Sex))%>%layout(xaxis=list(title="3rd Class",font=t))%>%layout(yaxis=yaxs),
filter(data,Class=="Crew")%>%addnewline("Sex","Age")%>%plot_ly(x=~Age,y=~Survival_Rate)%>%add_lines(showlegend=FALSE)%>%add_markers(color=~as.factor(Sex),showlegend=FALSE,color=~as.factor(Sex))%>%layout(xaxis=list(title="Crew",font=t)),shareY=TRUE,nrows=2,shareX=TRUE,titleX = TRUE
)%>%layout(title="Titanic Survival Rate",annotations=list(list(x=0.2,y=0.5,text="1st Class",showarrow=F,xref="paper",yref="paper"),list(x=0.8,y=0.5,text="2nd Class",showarrow=F,xref="paper",yref="paper")))
```

## Observations

Based on these 4 plots, we can observe 

- 1st Class people do have the best survival rate on all groups of people.
- All children  and most females(>86%) from 1st Class, 2nd Class and Crew group are saved. 
- But in 3rd class less than half children and females are saved
- Adult male of 1st Class have the highest survival rate (33%) followed by adult male from Crew group (22%). And Adult male from 2nd Class have theh lowest survival rate which is only 8%. 

## Thanks!




